\plaintitle

### 2016-08-04 drafts/labor/cases.tex
wed

\subsection{What forms of work design and worker management are viable?}

>>>>

\subsection{What forms of work design and worker management are viable?}
\begin{itemize}
  \item researchers have looked at how to increase worker productivity
  (e.g. finding the maximal speed at which gig workers can be expected to work before making errors)
  \cite{measuringCrowdsourcingCheng}.
  \item we've also seen people ``embrace error''
  \cite{embracingErrorKrishna}.
  \item still other research has looked into ways to sandbox workers from the context of their work 
  \item but scholarship looking into the design and management of work and workers isn't new;
  lots of research into getting pieceworkers to do work more quickly
  \cite{seymour1954manual}.
  \item Researchers have even asked the age old question of \textit{what motivates} pieceworkers
  (echoing similar research on Wikipedia and Mechanical Turk)
  \cite{roy1953work,Nov:2007:MW:1297797.1297798,kaufmann2011more}
\end{itemize}
